Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-14 ms.tex
more

%list of figures : 
% posterior surface for some pixel, with samples from markov chain overplotted
%    --> also overplot output best-fit (T,I545) and unctertainty estimate
% plot for some set of pixels of SED overlaid with best-fit two-component model
%    --> done in Python instead of IDL
%    --> overlay 
% plot of resulting T2 and tau
% plots of full-sky residuals relative to our model ?
%  ---> and for lower-frequency bands to emphasize that FDS99 is better for
%       extrapolating towards mm wavelengths

@@

\subsection{Smoothing}
We wish to simultaneously fit \verb|i100| along with four \PLANCK~bands. To 
properly combine these maps, they must have the same PSF. \verb|i100|, with its
$6.1'$ symmetric Gaussian PSF, is the lowest-resolution map we have included. 
To match PSFs, we have therefore smoothed each of the \PLANCK~maps under 
consideration to $6.1'$ resolution by considering each native map to have
a symmetric Gaussian beam and smoothing by the appropriate symmetric Gaussian
such that the resulting map has a FWHM of $6.1'$. The FWHM we assign to the 
native \PLANCK~maps is taken from \cite{planckbeam}, specifically $5.01'$ for
217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.

@@

\begin{equation}
\sigma_{\nu_i} = \sqrt{c^2_{\nu_i}I^2_{\nu_i} + c^2_{\nu_i}CMB_{\nu_i} + }
\end{equation}

This error budget is based on \cite{planckdust} Equation 7. $c_{\nu_i}$ is the 
multiplicative calibration uncertainty for the intensity in each band, and we 
have adopted the values listed in \cite{planckdust} Table 1. We have adopted 
$c_{217 GHz}$ = XX. In order to obtain reasonable fitting results at high 
latitude where the data is noisy, we include a prior on $T_2$:

@@

%provide maps at multiple different nsides ?
%   -> if so, actually smooth the maps before rebinning, or leave 
%      undersampled?

>>>>

%list of figures : 
% posterior surface for some pixel, with samples from markov chain overplotted
%    --> also overplot output best-fit (T,I545) and unctertainty estimate
% plot for some set of pixels of SED overlaid with best-fit two-component model
%    --> done in Python instead of IDL
%    --> overlay 
% plot of resulting T2 and tau
% plots of full-sky residuals relative to our model ?
%  ---> and for lower-frequency bands to emphasize that FDS99 is better for
%       extrapolating towards mm wavelengths
% zoom-in of region with interesting dust showing :
%  SFD T map, two-component T map, Planck team one-component T map

@@

\subsection{Smoothing}
We wish to simultaneously fit \verb|i100| along with four \PLANCK~bands. To 
properly combine these maps, they must have the same point spread function 
(PSF). \verb|i100|, with its $6.1'$ symmetric Gaussian PSF, is the 
lowest-resolution map we have included. To match PSFs, we have therefore 
smoothed each of the \PLANCK~maps under consideration to $6.1'$ resolution by 
considering each native map to have a symmetric Gaussian beam and smoothing by 
the appropriate symmetric Gaussian such that the resulting map has a FWHM of 
$6.1'$. The FWHM we assign to the native \PLANCK~maps is taken from 
\cite{planckbeam}, specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, 
$4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.

@@

\begin{equation}
\sigma_{\nu_i} = \sqrt{c^2_{\nu_i}I^2_{\nu_i} + c^2_{\nu_i}CMB^2_{\nu_i} + (\delta O_{\nu_i})^2 + n^2_{\nu_i}}
\end{equation}

% what about the instrumental noise n_{\nu_i} ---> can't find anything
% in planck literature

This error budget is based on \cite{planckdust} Equation 7. $c_{\nu_i}$ is the 
multiplicative calibration uncertainty for the intensity in each band. We 
have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} Table 1. For 
the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from Table 11 of 
\cite{planckcalib}. In order to obtain reasonable fitting results at high 
latitude where the data is noisy, we include a prior on $T_2$:

@@

%provide maps at multiple different nsides ?
%   -> if so, actually smooth the maps before rebinning, or leave 
%      undersampled?
% provide uncertainty maps for tau and T2 ??

\subsection{Limitations}
% CIBA !!!
% IRAS missing so that parts of sky not truly 6.1' resolution map
